\Russell's Metatheoretic Study - Abstract

### 2006-06-02 papers/ICFP'06-wmm/abstract-only.tex
li'll fixes

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle

@@

\item Correction of the interpretation: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

@@

{\bf Disclaimer}: this is a work in
progress ; to this day we have proved elimination of transitivity and
subject reduction should follow soon.

>>>>

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  \url{sozeau@lri.fr} -- \url{http://www.lri.fr/~sozeau}}
\begin{document}
\maketitle

@@

\item Correction of the interpretation: the target system has
  metavariables, introducing a second, \emph{unusual} kind of variable
  binding.
\end{itemize}

@@

{\bf Disclaimer}: this is a work in
progress ; to date we have proved elimination of transitivity and
subject reduction should follow soon.
